---
title: "Coral_Model"
author: "Sarah Morris & Lindsey Pekurny"
date: "10/14/2020"
output: html_document
---

**Part A**
**Our Consensus Flow Diagram**

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

knitr::include_graphics('/Users/sarahmorris/Desktop/MentalModeler__Model__[author]__2020-10-14_14_06_21.png')


```

Number 3: Create a new flow chart and define variables
Note - Parrotfish CANNOT eat algal turf in this model

Variables

  a -> rate of macro-algae growth over coral
  gamma -> rate of macro-algae growth over algal turf
  d -> coral death rate
  r -> rate of coral growth of algal turf
  s -> ??
  
Parrot fish carrying capacity = K(C). K(C) = C, which is overall coral cover.


Number 4: Program the Model

-What do we want our model to show?
  Growth rates for all 4 organisms? Or just for coral?


```{r} 
### Copied code from problem 2. I am going to modify this. First, I'm going to see if I can run all equations at once

require(deSolve)
## Loading required package: deSolve
# Initial values

state <- c(N=50.5)   ### I think 10 and 50 may be an equilibrium point
times <- seq(0,100,by=1)

# Parameters
parameters <- c(b = 2.4,c=0.02,M=50,d=0.2)

# Model
sterile_insect <- function(t,state,parameters){
  with(as.list(c(state,parameters)),{
       dN <- b*N/(N+M) - d - c*N
      list(c(dN))   
  })}

# Solve model and plot results
out1 <- ode(y = state,times=times,func=sterile_insect,parms=parameters)
par(mfrow=c(1,1))
plot(out1[,1],out1[,2],ylab='N',xlab='time',las=1, pch = 19)

```
**#3**
**Flow diagram for coral reef system**

#insert new model here
#Explain what mechanisms might explain which arrows point where in the flow diagram
#insert table with completed parameter descriptions

**#4**
#program the model

**#5**
#Produce figures and design analyses to address the following questions: 
**(a) What are the long-term dynamics of the system with the default parameters given below?**
**(b) What are the most important parameters in determining the long-term dynamics?**

Testing
test2
test3
